%-------------------------
% Resume in Latex
% Author : Jake Gutierrez
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
%\usepackage[sfdefault]{FiraSans}
%\usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}
\usepackage[sfdefault]{inter}


% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}


\usepackage{calc} % added
\newcommand{\resumeSubSubheadingLeft}[2]{% % added
\begin{description}[leftmargin=!,labelwidth=\widthof{\small\bfseries #1}]
    \item[\small #1]{\textit{\small  #2}}
\end{description}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------

\begin{center}
    \textbf{\Huge \scshape Bennett Zug} \\ \vspace{1pt}
    \small 919-798-1090 $|$ \href{mailto:bennettzug@gmail.com}{\underline{bennettzug@gmail.com}} $|$ 
    \href{https://www.linkedin.com/in/bennett-zug/}{\underline{https://www.linkedin.com/in/bennett-zug/}} $|$
    \href{https://github.com/bennettzug}{\underline{https://github.com/bennettzug}}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Appalachian State University}{August 2022 -- Present}
      {B.S in Computer Science, Minor in Mathematics $|$ GPA: 3.9/4.0 (Major), 3.5/4.0 (Overall)}{Boone, NC}
      \resumeSubSubheadingLeft% added <<<<<<<<<<<<<<<
    	{Relevant Coursework:}{Data Structures, Introduction to Theoretical Computer Science, Discrete Math, Linear Algebra}
      
    
  \resumeSubHeadingListEnd


%-----------PROJECTS-----------
\section{Projects}

    \resumeSubHeadingListStart
     \resumeProjectHeading
          {\textbf{EquiB} $|$ \emph{React, Firebase}}{Hackathon Project}
          \resumeItemListStart
            \resumeItem{Collaborated in a team to develop a React web app called EquiB at HackNC 2023 with the goal of demonstrating a blockchain-based banking concept.}
            \resumeItem{Won the "Best Use of Circle" prize category for utilizing Circle's USDC stablecoin platform in the proposed application design.}
            
         \resumeItemListEnd
    \resumeSubHeadingListEnd
	
    \resumeSubHeadingListStart
     \resumeProjectHeading
          {\textbf{Predicting Median Housing Prices} $|$ \emph{R, Python}}{}
          \resumeItemListStart
            \resumeItem{Performed web scraping using Python and Selectolax HTML parser to collect structured data from websites into a CSV format, enabling efficient data acquisition for analysis.}
            \resumeItem{Developed a linear regression model in R to predict median housing prices across U.S. metropolitan areas based on various socioeconomic factors.}
            \resumeItem{Evaluated model performance using metrics like R-squared and RMSE, compared against other architectures like random forests, and visualized results with ggplot2.}
         \resumeItemListEnd
    \resumeSubHeadingListEnd
    
     \resumeSubHeadingListStart
     \resumeProjectHeading
          {\textbf{MatrixOCR} $|$ \emph{Python, OpenCV, Tesseract, SymPy}}{}
          \resumeItemListStart
            \resumeItem{Developed a Python command-line tool to automatically extract mathematical matrices from images by integrating OpenCV for image pre-processing and Tesseract OCR engine, enabling efficient data extraction from screenshots.}
            \resumeItem{Leveraged SymPy library to perform Gauss-Jordan elimination and other matrix operations on the extracted matrices.}
            \resumeItem{Optimized image pre-processing pipeline using OpenCV functions like thresholding and contour detection to improve matrix detection accuracy to $>$95\%}
            
         \resumeItemListEnd
    \resumeSubHeadingListEnd
    
         \resumeSubHeadingListStart
     \resumeProjectHeading
          {\textbf{\href{https://www.class-search.com}{\underline{class-search.com}}} $|$ \emph{Python, Flask, PyTorch, Svelte, PostgreSQL}}{}
          \resumeItemListStart
          		\resumeItem{Developed a web application to search and discover relevant university courses by computing vector embeddings for over 30,000 gathered course descriptions from multiple instututions using PyTorch and pre-trained language models.}
          		\resumeItem{Built a Flask backend to efficiently match user queries against the corpus of course embeddings by leveraging PostgreSQL with the pgvector extension for fast approximate nearest neighbor search.}
          		\resumeItem{Designed an interactive Svelte frontend with features like university selection, course search within institutions, and dynamic content updates to provide a seamless user experience.}
          		\resumeItem{Deployed the Flask web server to production using Gunicorn and Nginx, ensuring high availability and sub-200ms search latency through optimized vector search without external API calls.}

         \resumeItemListEnd
    \resumeSubHeadingListEnd
	

%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart

    \resumeSubheading
      {Summer Technology Assistant}{Summers, 2018--2023}
      {St Timothy's School}{Raleigh, NC}
      \resumeItemListStart
        \resumeItem{Managed Google accounts and Chrome devices for the middle school of over 200 students, utilizing automated account provisioning to reduce manual effort by 80\%.}
        \resumeItem{Demonstrated strong problem-solving abilities by independently troubleshooting and resolving technology issues reported by staff while providing clear guidance.}
        \resumeItem{Troubleshooted technology problems from other staff.}
        \resumeItem{Grew into a leadership role over successive summers by proactively identifying process improvements to enhance overall technology support efficiency.}
      \resumeItemListEnd
      

    \resumeSubheading
      {Youth Coach and Event Belayer}{October 2021 -- January 2023}
      {Triangle Rock Club}{Raleigh, NC}
      \resumeItemListStart
        \resumeItem{Effectively communicated safety instructions and climbing techniques to youth and adult climbers in a clear and engaging manner to ensure a secure and enjoyable experience.}
        \resumeItem{Managed after-school youth programs by coordinating activities, delegating tasks to staff, and ensuring a structured yet fun experience for participants.}
      \resumeItemListEnd

  \resumeSubHeadingListEnd



%-------------ORGANIZATIONS-------------

\section{Organizations}
\resumeSubHeadingListStart

\resumeSubheading
      {FTC 2901 Member}{August 2018 -- May 2020}
      {Cardinal Gibbons High School}{Raleigh, NC}
      \resumeItemListStart
      	\resumeItem{Contributed as a programmer on the FIRST Tech Challenge robotics team to develop autonomous driving capabilities for the competition robot using Java.}
      	\resumeItem{Collaborated in a team environment to enhance the robot's movement code quality through code refactoring}
        \resumeItem{Played a key role in enabling the team to qualify for FTC Nationals by delivering robust autonomous navigation software adhering to competition guidelines.}
      \resumeItemListEnd

\resumeSubHeadingListEnd



%-----------TECHNICAL SKILLS-----------


\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: Java, Python, R, SQL, HTML/CSS, \LaTeX} \\
     
    \textbf{Frameworks/Libraries}{: Svelte, Flask, PyTorch, NumPy, Pandas, OpenCV}\\
    \textbf{Tools/Platforms}{: Git, Vim, VS Code, PostgreSQL}
    }}
 \end{itemize}


%-------------------------------------------
\end{document}